\chapter{References}
\section{Research Papers}
\begin{enumerate}
    \item Paolo Falcone, Francesco Borrelli, Jahan Asgari, Hongtei Eric Tseng. Predictive Active Steering Control for Autonomous Vehicle Systems. \textit{IEEE Transactions on Control Systems Technology}, 15(3), 2007.

    Link: \href{https://ieeexplore.ieee.org/document/4162483}{https://ieeexplore.ieee.org/document/4162483}
    \item Daisuke Akasaka, Taku Takahama. Model Predictive Control Approach to Design Practical Adaptive Cruise Control for Traffic Jam. \textit{International Journal of Automotive Engineering}, 9(3), 2018. 

    Link: \href{https://www.jstage.jst.go.jp/article/jsaeijae/9/3/9_20184095/_article}{https://www.jstage.jst.go.jp/article/jsaeijae/9/3/9\_20184095/\_article}
    \item Trieu Minh Vu, Reza Moezzi, Jindrich Cyrus, Jaroslav Hlava. Model Predictive Control for Autonomous Driving Vehicles. \textit{Electronics, MDPI Open Access Journals}, 10, 2021. 

    Link: \href{https://doi.org/10.3390/electronics10212593}{https://doi.org/10.3390/electronics10212593}
\end{enumerate}

\section{Other Resources}
\begin{enumerate}
    \setcounter{enumi}{3}
    \item Melda Ulusoy (2023). Designing an MPC controller with Simulink, MATLAB Central File Exchange. Retrieved October 11, 2023.

    Link: \href{https://www.mathworks.com/matlabcentral/fileexchange/68992-designing-an-mpc-controller-with-simulink}{https://www.mathworks.com/matlabcentral/fileexchange/68992}

    \item Melda Ulusoy (2023). Adaptive MPC Design with Simulink, MATLAB Central File Exchange. Retrieved October 11, 2023.

    Link: \href{https://www.mathworks.com/matlabcentral/fileexchange/68939-adaptive-mpc-design-with-simulink}{https://www.mathworks.com/matlabcentral/fileexchange/68939}
    \item Vehicle Path Tracking using Model Predictive Control (Improving Your Racecar Development), Mathworks GitHub Repository, 2022.

    Link: \href{https://in.mathworks.com/videos/vehicle-path-tracking-using-model-predictive-control-1647494222398.html}{https://in.mathworks.com/videos/vehicle-path-tracking-using-model-predictive-control}
    \newpage
    \item Obstacle Avoidance Using Adaptive Model Predictive Control, Mathworks Help Center (Automated Driving Applications, Model Predictive Control).

    Link: \href{https://in.mathworks.com/help/mpc/ug/obstacle-avoidance-using-adaptive-model-predictive-control.html}{https://in.mathworks.com/help/mpc/ug/obstacle-avoidance-using-adaptive-model-predictive-control}
    \item Multi-Purpose-MPC, Online GitHub Repository owned by \href{https://github.com/matssteinweg}{\texttt{matssteinweg}}, 2019.

    Link:
    \href{https://github.com/matssteinweg/Multi-Purpose-MPC}{https://github.com/matssteinweg/Multi-Purpose-MPC}
    \item Automated Driving using Model Predictive Control, Mathworks Help Center (Model Predictive Control Toolbox, Automated Driving Applications)

    Link: \href{https://in.mathworks.com/help/mpc/ug/automated-driving-using-model-predictive-control.html}{https://in.mathworks.com/help/mpc/ug/automated-driving-using-model-predictive-control}
    \item Jarrod M. Snider, Automatic Steering Methods for Autonomous Automobile Path Tracking, \textit{Robotics Institute, Carnegie Mellon University}, 2009.

    Link: \href{https://www.ri.cmu.edu/pub_files/2009/2/Automatic_Steering_Methods_for_Autonomous_Automobile_Path_Tracking.pdf}{https://www.ri.cmu.edu/pub\_files/2009/2/Automatic\_Steering\_Methods\_for\_Autonomous\_Automobile\newline\_Path\_Tracking.pdf}
    \item 
\end{enumerate}